\documentclass[12pt,a4paper,twocolumn]{article}

\usepackage[english]{babel} 		%% englische Sprache

\usepackage[latin1,applemac]{inputenc}	%% deutsche Umlaute wie normale
 					%% Buchstaben verwenden 
 					%% (ansonsten muesste ‰ durch a getippt werden)
\usepackage{a4wide} 			%% kleinere Seitenränder

\usepackage{amssymb,amsthm,amsfonts, amsmath}
								%% diverse Matheerweiterungen, z.B. \implies
 								%% diverse Matheerweiterungen, z.B. \mathbb{R}
%\usepackage{stmaryrd} 			%% weitere Symbole
\usepackage{epsfig} 			%% um eps-Dateien einzubinden (\epsfig{file=...})
\usepackage{longtable} 			%% fuer Tabellen ueber mehrere Seiten
\usepackage{color}
\usepackage{hyperref}
\usepackage{dsfont}
\usepackage{caption}
\captionsetup[table]{name=Cache tables}

\title{ \textit{Some super concise and informative title} \\ Data Analysis Project for \\ \textit{Machine Learning: Basic Principles}}
%\author{Héctor Laria Mantecón and Maximilian Proll}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}

\textit{
Precise summary of the whole report, previews the contents and results. Must be a single paragraph between 100 and 200 words.
}

\end{abstract}

\section{Introduction}

\textit{
Background, problem statement, motivation, many references, description of contents. Introduces the reader to the topic and the broad context within which your research/project fits
\begin{itemize}
\item What do you hope to learn from the project?
\item What question is being addressed?
\item Why is this task important? (motivation)
\end{itemize}
Keep it short (half to 1 page).
}

\section{Data analysis}

\textit{
Briefly describe data (class distribution, dimensionality) and how will it affect classification. Visualize the data. Don’t focus too much on the meaning of the features, unless you want to.
\begin{itemize}
\item Include histograms showing class distribution.
\end{itemize}
}

\section{Methods and experiments}

\textit{
Explain your whole approach (you can include a block diagram showing the steps in your process).
\begin{itemize}
\item What methods/algorithms, why were the methods chosen.
\item What evaluation methodology (cross CV, etc.).
\end{itemize}
}

\section{Results}

\textit{
Summarize the results of the experiments without discussing their implications.
\begin{itemize}
\item Include both performance measures (accuracy and LogLoss).
\item How does it perform on kaggle compared to the train data.
\item Include a confusion matrix.
\end{itemize}
}

\section{Discussion/Conclusions}

\textit{
Interpret and explain your results
\begin{itemize}
\item Discuss the relevance of the performance measures (accuracy and LogLoss) for
imbalanced multiclass datasets.
\item How the results relate to the literature.
\item Suggestions for future research/improvement.
\item Did the study answer your questions?
\end{itemize}
}

\section{References}

\textit{List of all the references cited in the document
}

\section{Appendices}

\textit{Additional information that is not essential to explain your findings, but supports your work. For example, source code, additional images, mathematical derivations, etc.
If you include source code, don’t include the whole code, focus only on the most important parts, for example, a function implementing a specific algorithm
}


\end{document}